%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
% \usepackage[colorlinks = true, urlcolor  = blue]{hyperref}
% \input{glyphtounicode}
\usepackage{datetime} %日期


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\LARGE
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      % \textit{\small#1} & \textit{\small #2} \\
      \textbf{#1} & #2 \\
    \end{tabular*}
    \vspace{-5pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #2 \\
      {\small#3} & {\small #4} \\
      {\small#5} & {\small #6} \\
      % \multicolumn{2}{l}{\small#7}
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\renewcommand{\today}{\number\year-\number\month-\number\day }

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge Enming Liang} \\ 
    \vspace{10pt}
    \faMobile \hspace{.5pt} \href{tel:85254958047}{+852-54958047}
    $|$
    \faAt \hspace{.5pt} \href{eliang4-c@my.cityu.edu.hk}{eliang4-c@my.cityu.edu.hk}
    $|$
    \faMapMarker \hspace{.5pt} \href{d}{Hong Kong} 
\\   \vspace{5pt}
    \faGoogle \hspace{.5pt} \href{https://scholar.google.com.sg/citations?user=Todfu6AAAAAJ&hl=zh-CN}{Google Scholar}
    $|$
    \faGithub \hspace{.5pt} \href{https://emliang.github.io/}{Personal Webpage}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/enming-liang-95b5b216a/}{LinkedIn}
\\    \vspace{10pt}
     Updated: \today
\end{center}




%----------- Research Interests -----------

\section{\LARGE Research Interests}
  \vspace{5pt}
  % \hspace{4pt}
    {Machine Learning for Constrained Optimization, with Applications in Transportation, Energy, and Climate.}{}

%----------- EDUCATION -----------

\section{\LARGE Education}
  \vspace{5pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {City University of Hong Kong}{Hong Kong}
      {Ph.D. $|$ Department of Data Science}{2021/09 \textbf{--} 2024/10}
      {Advisor: Prof. Minghua Chen}{}
      \resumeItemListStart
          \resumeItem{Thesis: Machine Learning for Constrained Optimization: Solution Feasibility and Multi-valued Mapping}
      \resumeItemListEnd
  \vspace{5pt}

    \resumeEducationHeading
    {Sun Yat-sen University}{Guangzhou}
    {B.Eng. $|$ School of Intelligent Systems Engineering}{2016/09 \textbf{--} 2020/07}
    {Advisor: Prof. Renxin Zhong}{}
    \resumeItemListStart
        \resumeItem{{GPA}: 91/100, {Rank}: 1/47}
        \resumeItem{Outstanding Graduation Thesis at SYSU: Supply and Demand Management in Ride-sourcing Platform}
    \resumeItemListEnd
    % {Advisor: Prof. Renxin Zhong}{}
    % {{GPA}: 91/100, {Rank}: 1/47}{}
    % {Thesis: Supply and Demand Management in Ride-sourcing Platform}
    \vspace{5pt}

  \resumeSubHeadingListEnd


    
  


%----------- RESEARCH EXPERIENCE -----------
\section{\LARGE Research Experience}
\vspace{5pt}
  \resumeSubHeadingListStart
  

  \resumeSubheading
  {Cambridge University}{Cambridge}
  {Visiting Student $|$ Advisor: Prof. Srinivasan Keshav}{2024/05 \textbf{--} 2024/06}
    \resumeItemListStart
        \resumeItem{Resilience of European Transimission Grid under Extreme Weather}
    \resumeItemListEnd
    \vspace{5pt}


  \resumeSubheading
    {Microsoft Research Asia}{Beijing}
    {Research Intern $|$ Advisor: Dr. Li Zhao \& Dr. Lei Song }{2022/05 \textbf{--} 2022/09}%
      \resumeItemListStart
          \resumeItem{Data-Driven Optimization for Vehicle Routing Problem}
          \resumeItem{Multi-Agent Resource Optimization (MARO) platform}
      \resumeItemListEnd
      \vspace{5pt}
    
  \resumeSubheading
    {Huawei Noah’s Ark Lab}{Shenzhen}
    {Research Intern $|$ Advisor: Dr. Zhitang Chen}{2020/10 \textbf{--} 2021/04}
      \resumeItemListStart
          \resumeItem{Collaborative Optimization for Large-scale 4G LTE Cell Networks}
          \resumeItem{Scenario-based Optimization for High-Dimension 5G RF Parameters}
      \resumeItemListEnd
      \vspace{5pt}

  \resumeSubheading
    {Didi Chuxing \& SYSU Research Cooperation Program}{Guangzhou}
    {Research Assistant $|$ Advisor: Prof. Renxin Zhong}{2018/11 \textbf{--} 2020/05}
      \resumeItemListStart
      \resumeItem{A Multi-Agent Reinforcement Learning Approach for Online Vehicle Dispatching}
      \resumeItem{Dynamic Spatial-Temporal Pricing for Supply-demand Regulations of Ride-sourcing Market}
    \resumeItemListEnd
    \vspace{5pt}

    \resumeSubheading
        {Guangdong Key Laboratory of Intelligent Transportation Systems}{Guangzhou}
        {Research Assistant $|$ Advisor: Prof. Renxin Zhong}{2018/04 \textbf{--} 2018/10}
          \resumeItemListStart
              \resumeItem{The Calibration of First-Order Macroscopic Traffic Models Using MF-CEM}
        \resumeItemListEnd
        \vspace{5pt}

  \resumeSubHeadingListEnd














%----------- Publication -----------
\section{\LARGE Conference Publications}
\vspace{5pt}
\resumeSubHeadingListStart
    \small{\item{
      {Jiaqi Yang, \underline{\textbf{Enming Liang}}, Zicheng Su, Zhichao Zou, Zhen Peng, Jiecheng Guo, Kun An, Wanjing Ma. DFF: Decision-Focused Fine-tuning for Smarter Predict-then-Optimize with Limited Data. In Proceedings of the AAAI Conference on Artificial Intelligence (\textbf{AAAI'2025}).}\\ 
      \vspace{10pt}

      {Chenghao Liu, \underline{\textbf{Enming Liang}}, Minghua Chen. Characterizing ResNet's Universal Approximation Capability. In Proceedings of the Forty-first International Conference on Machine Learning (\textbf{ICML'2024}).}\\ 
      \vspace{10pt}

      {\underline{\textbf{Enming Liang}}, Minghua Chen. Generative Learning for Solving Non-Convex Problem with Multi-Valued Input-Solution Mapping. In Proceedings of the Twelfth International Conference on Learning Representations (\textbf{ICLR'2024}).}\\ 
      \vspace{10pt}


      {\underline{\textbf{Enming Liang}}, Minghua Chen, Steven H. Low. Low Complexity Homeomorphic Projection to Ensure Neural-Network Solution Feasibility for Optimization over (Non-)Convex Set. In Proceedings of the Fortieth International Conference on Machine Learning (\textbf{ICML'2023}).}\\ \vspace{10pt}


      {Yunping Huang, Nan Zheng, \underline{\textbf{Enming Liang}}, Shu-Chien Hsu, Renxin Zhong. An Approximate Dynamic Programming Approach to Vehicle Dispatching and Relocation using Time-Dependent Travel Times. In 2023 IEEE 26th International Conference on Intelligent Transportation Systems (\textbf{ITSC'2023}).}\\ 
      \vspace{10pt}

      {\underline{\textbf{Enming Liang}}, Zicheng Su, Chilin Fang, Renxin Zhong. OAM: an Option-Action Reinforcement Learning Framework for Universal Multi-Intersection Control. In Proceedings of the AAAI Conference on Artificial Intelligence (\textbf{AAAI'2022}). \textbf{Oral}.}\\ 
      \vspace{10pt}

      % {Renxin Zhong, Kexin Wen, Chilin Fang, \underline{\textbf{Enming Liang}}. Real-time Multi-Resource Jointed Scheduling of Container Terminals with Uncertainties using a Reinforcement Learning Approach. In 2022 13th Asian Control Conference (\textbf{ASCC}). IEEE. 2022} \\
      %  \vspace{10pt}
    }}
  \vspace{5pt}
  \resumeSubHeadingListEnd


\section{\LARGE Journal Publications}
\vspace{5pt}
\resumeSubHeadingListStart
  \small{\item{
    {\underline{\textbf{Enming Liang}}, Minghua Chen, Steven H. Low. Homeomorphic Projection to Ensure Neural-Network Solution Feasibility for Constrained Optimization. Journal of Machine Learning Research (\textbf{JMLR}). 2024}\\ \vspace{10pt}

    Zicheng Su, Andy H.F. Chow, Chilin Fang, \underline{\textbf{Enming Liang}}, Renxin Zhong. Hierarchical Control for Stochastic Network Traffic with Reinforcement Learning. Transportation Research Part B: Methodological (\textbf{TRB}). 2023. \\ 
    \vspace{10pt}

    {\underline{\textbf{Enming Liang}}, Kexin Wen, William H.K. Lam, Agachai Sumalee, Renxin Zhong. An Integrated Reinforcement Learning and Centralized Programming Approach for Online Taxi Dispatching. IEEE Transactions on Neural Networks and Learning Systems (\textbf{TNNLS}). 2021.} \\
    \vspace{10pt}

    {Andy H.F. Chow, Zicheng Su, \underline{\textbf{Enming Liang}}, Renxin Zhong. Adaptive Signal Control for Bus Service Reliability with Connected Vehicle Technology via Reinforcement Learning. Transportation Research Part C: Emerging Technologies (\textbf{TRC}). 2021.} \\ 
    \vspace{10pt}

    {Zicheng Su, Andy H.F. Chow, Nan Zheng, Yunping Huang, \underline{\textbf{Enming Liang}}, Renxin Zhong. Neuro-Dynamic Programming for Optimal Control of Macroscopic Fundamental Diagram Systems. Transportation Research Part C: Emerging Technologies (\textbf{TRC}). 2020.} \\
    \vspace{10pt}
  }}
  \vspace{5pt}
\resumeSubHeadingListEnd



\section{\LARGE Working Papers}
\vspace{5pt}
\resumeSubHeadingListStart
  \small{\item{
    {\underline{\textbf{Enming Liang}} and Minghua Chen. Efficient Bisection Projection to Ensure Neural-Network Solution Feasibility for Constrained Optimization over General Set. (Under review). 2024.}\\ \vspace{5pt}
  }}
  \small{\item{
    {\underline{\textbf{Enming Liang}}, Minghua Chen, and Srinivasan Keshav. European Electricity Grids May Exhibit Heatwave-induced Capacity Bottlenecks. (Under review). 2024.}\\ \vspace{5pt}
  }}
  \small{\item{
    Min Zhou, {\underline{\textbf{Enming Liang}}, Minghua Chen, and Steven Low. Partially Permutation-Invariant Neural Network for Solving Two-Stage Stochastic AC-OPF Problem. (Under review). 2024.}\\ \vspace{5pt}
  }}
  \vspace{5pt}
\resumeSubHeadingListEnd






%----------- Proposal & Grants -----------
\section{\LARGE Grants \& Funds}
\vspace{5pt}
\resumeSubHeadingListStart

\resumeSubheading
{CCF-DiDi GAIA Collaborative Research Funds 2024}{Beijing}
{Co-PI $|$ working with Dr. Zicheng Su (Tongji University)}{2024/07 \textbf{--} 2025/07}
  \resumeItemListStart
      \resumeItem{Optimal Subsidy Design for Ride-Sourcing Platform}
\resumeItemListEnd
\vspace{5pt}

\resumeSubheading
{CCF-DiDi GAIA Collaborative Research Funds 2023}{Beijing}
{Co-PI $|$ working with Dr. Zicheng Su (Tongji University)}{2023/07 \textbf{--} 2024/07}
  \resumeItemListStart
      \resumeItem{Decision-Focused Learning for Ride-Sourcing Platform}
\resumeItemListEnd
\vspace{5pt}
\resumeSubHeadingListEnd




%----------- AWARDS & ACHIEVEMENTS -----------
\section{\LARGE Tutorial \& Teaching}
\vspace{5pt}
\resumeSubHeadingListStart
\resumeSubheading
{\href{https://githubtocolab.com/climatechange-ai-tutorials/optimal-power-flow/blob/main/AI_for_Optimal_Power_Flow.ipynb}{AI for Optimal Power Flow Tutorial}}
{\href{https://www.climatechange.ai/tutorials?}{Climate Change AI Summer School}}
{\underline{\textbf{Enming Liang}}, 
Priya L. Donti, and 
Minghua Chen}{2024/07 \textbf{--} 2024/08}
%   \resumeItemListStart
%       \resumeItem{\href{https://githubtocolab.com/climatechange-ai-tutorials/optimal-power-flow/blob/main/AI_for_Optimal_Power_Flow.ipynb}{AI for Optimal Power Flow Tutorial}}
% \resumeItemListEnd

\vspace{10pt}
\resumeSubSubheading
{Teaching Assistant at CityU, HK}{2021-2024}
\resumeItemListStart
\resumeItem{2021/22 Semester B}{$|$  }{ SDSC3060 Operations Research}
\vspace{1pt}
\resumeItem{2022/23 Semester A}{$|$  }{ SDSC3019 Intro to Networked Life \& DS}
\vspace{1pt}
\resumeItem{2022/23 Semester B}{$|$  }{ SDSC6014 Networked Life \& Data Science}
\vspace{1pt}
\resumeItem{2023/24 Semester B}{$|$  }{ SDSC6014 Networked Life \& Data Science}
\resumeItemListEnd

\vspace{5pt}
\resumeSubHeadingListEnd


%----------- AWARDS & ACHIEVEMENTS -----------


\section{\LARGE Competition Prizes}
\vspace{5pt}
\resumeSubHeadingListStart
\resumeSubheading
{\href{https://www.biendata.xyz/competition/kdd_didi/winners/}{KDD CUP: Learning to Dispatch and Reposition on a Mobility-on-Demand Platform}}{2020}
{Solo winner $|$ Top 2 (0.1\%) in Task 1 $|$ Top 5 (0.2\%) in Task 2}{}
\vspace{5pt}

\resumeSubheading
{ICAPS Dynamic Pickup and Delivery Problem Competition}{2021}
{Silver Prize (0.2\%)}{}
\vspace{5pt}

\resumeSubheading
{MeiTuan 1st Low-Altitude Economy Flight Management Challenge}{2024}
{Silver Prize (1\%)}{}
\vspace{5pt}


\resumeSubHeadingListEnd






%----------- AWARDS & ACHIEVEMENTS -----------
\section{\LARGE Awards \& Honors}
\vspace{5pt}
\resumeSubHeadingListStart

\resumeSubSubheading
{{Top Reviewer Award in NeurIPS 2024}}{2024}
\vspace{1pt}

\resumeSubSubheading
{Excellence Award in \textit{Star of Tomorrow Internship Program}, MSRA}{2022}
\vspace{1pt}

\resumeSubSubheading
{Research Tuition Scholarship at CityU, HK}{2022 \& 2023}
\vspace{1pt}

\resumeSubSubheading
{Outstanding Undergraduate Thesis at SYSU}{2020}
\vspace{1pt}

\resumeSubSubheading
{National Scholarship in China}{2020}
\vspace{1pt}
 
\resumeSubHeadingListEnd















\section{\LARGE Services}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeSubheading
{{Conference Reviewer}}{2023-2025}
{}{}
\vspace{-15pt}
\resumeItemListStart
\resumeItem{AAAI}{2023}{ 2024}{ 2025}
\resumeItem{ICLR}{2025}
\resumeItem{ICML}{2025}
\resumeItem{NeurIPS}{2024}
\resumeItem{AISTATS}{2025}
\resumeItemListEnd
\resumeSubHeadingListEnd



%----------- SKILLS -----------

% \section{Skills}
%   \vspace{2pt}
%   \resumeSubHeadingListStart
%     \small{\item{
%         \textbf{Languages:}{ Chinese (Native), English (TOEFL 107, GRE 325)} \\ \vspace{3pt}
%         \textbf{Programming:}{ Python, MATLAB} \\ \vspace{3pt}
%     }}
%   \resumeSubHeadingListEnd



%----------- RELEVANT COURSEWORK -----------

% \section{Relevant Coursework}
%   \vspace{2pt}
%   \resumeSubHeadingListStart
%     \small{\item{
%         \textbf{Major coursework:}{ Calculus I-II, Matrix Theory, Differential Equations, Materials Science, Electrical Circuits I-II, Digital System Design, Numerical Methods, Probability Theory, Electronics I-II, Signals and Systems, Electromagnetic Field Theory, Energy Conversion, System Dynamics and Control, Communication Engineering} \\ \vspace{3pt}
        
%         \textbf{Minor coursework:}{ Discrete Computational Structures, Introduction to Object-Oriented Programming, Data Structures and Algorithms}
%     }}
%   \resumeSubHeadingListEnd



%----------- CERTIFICATES -----------

% \section{Certificates}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Procter \& Gamble VIA Certificate Program}{Feb 2022}{Business Skills, Data and Digital Skills, Project Management and Personal Productivity}
    
  % \resumeSubHeadingListEnd



%----------- ORGANIZATIONS -----------

% \section{Organizations}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Institute of Electrical and Electronics Engineers (IEEE)}{Feb 2022 -- Present}{Student Member}
    
  % \resumeSubHeadingListEnd



%----------- HOBBIES -----------

% \section{Hobbies}
  % \resumeSubHeadingListStart
    % \small{\item{Swimming, Fitness, Eight-ball}}
  % \resumeSubHeadingListEnd



%----------- REFERENCES -----------

% \section{References}
  % \resumeSubHeadingListStart
    
  % \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
