%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
% \usepackage[colorlinks = true, urlcolor  = blue]{hyperref}
% \input{glyphtounicode}
\usepackage{datetime} %日期


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\LARGE
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      % \textit{\small#1} & \textit{\small #2} \\
      \textbf{#1} & #2 \\
    \end{tabular*}
    \vspace{-5pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #2 \\
      {\small#3} & {\small #4} \\
      {\small#5} & {\small #6} \\
      % \multicolumn{2}{l}{\small#7}
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\renewcommand{\today}{\number\year-\number\month-\number\day }

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge Enming Liang} \\ 
    \vspace{5pt}
    \faMobile \hspace{.5pt} \href{tel:85254958047}{+852-54958047}
    $|$
    \faAt \hspace{.5pt} \href{eliang4@cityu.edu.hk}{eliang4@cityu.edu.hk}
    $|$
    \faMapMarker \hspace{.5pt} \href{d}{Hong Kong} 
\\   \vspace{5pt}
    \faGoogle \hspace{.5pt} \href{https://scholar.google.com.sg/citations?user=Todfu6AAAAAJ&hl=zh-CN}{Google Scholar}
    $|$
    \faGithub \hspace{.5pt} \href{https://emliang.github.io/}{Personal Webpage}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/enming-liang-95b5b216a/}{LinkedIn}
\\    \vspace{5pt}
     Updated: \today
\end{center}




%----------- Research Interests -----------

\section{\LARGE Research Interests}
  \vspace{5pt}
    % {\Large \centering AI-Powered Optimization for Smarter Energy-Mobility Systems\\}{}
    {\large \centering AI for Optimization, Generative Models, 
    with Applications in Mobility, Energy, and Climate.\\}{}
  \vspace{5pt}
  
    % {\centering I aim to leverage artificial intelligence to develop intelligent decision frameworks that enhance synergy and resilience within integrated energy-mobility systems. This involves enabling high-penetration renewable energy integration, fostering EV-grid synergy, and constructing climate-resilient infrastructure.}{}
  % \hspace{4pt}
  % {\large My research goal is to develop parsimonious and theoretically grounded machine learning models that effectively manage critical infrastructure systems within physical and operational constraints.}{}
    

\section{\LARGE Employment}
\vspace{5pt}
\resumeSubHeadingListStart
  \resumeSubheading
    {Research Assistant Professor}{Hong Kong}
    {City University of Hong Kong $|$ College of Computing}{2025/01 \textbf{--} Present}
  \resumeSubHeadingListEnd
  \vspace{5pt}

%----------- EDUCATION -----------

\section{\LARGE Education}
  \vspace{5pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {City University of Hong Kong}{Hong Kong}
      {Ph.D. $|$ Department of Data Science}{2021/09 \textbf{--} 2024/10}
      {Advisor: Prof. Minghua Chen}{}
      \resumeItemListStart
          \resumeItem{Thesis: ML for Constrained Optimization: Solution Feasibility and Multi-valued Mapping}
      \resumeItemListEnd
  \vspace{5pt}

    \resumeEducationHeading
    {Sun Yat-sen University}{Guangzhou}
    {B.Eng. $|$ School of Intelligent Systems Engineering}{2016/09 \textbf{--} 2020/07}
    {Advisor: Prof. Renxin Zhong}{}
    \resumeItemListStart
        \resumeItem{{GPA}: 91/100, {Rank}: 1/47}
        \resumeItem{Thesis: Optimal Supply and Demand Management in Ride-sourcing Platform}
    \resumeItemListEnd

    \vspace{5pt}

  \resumeSubHeadingListEnd


    
  


%----------- RESEARCH EXPERIENCE -----------
\section{\LARGE Research Experience}
\vspace{5pt}
  \resumeSubHeadingListStart
  

  \resumeSubheading
  {Cambridge University}{Cambridge}
  {Visiting Researcher $|$ Advisor: Prof. Srinivasan Keshav}{2024/05 \textbf{--} 2024/06}
    \resumeItemListStart
        \resumeItem{Resilience of European Transimission Grid under Extreme Weather}
    \resumeItemListEnd
    \vspace{5pt}


  \resumeSubheading
    {Microsoft Research Asia}{Beijing}
    {Research Intern $|$ Advisor: Dr. Li Zhao \& Dr. Lei Song }{2022/05 \textbf{--} 2022/09}%
      \resumeItemListStart
          \resumeItem{Data-Driven Optimization for Vehicle Routing Problem}
          \resumeItem{Multi-Agent Resource Optimization (MARO) platform}
      \resumeItemListEnd
      \vspace{5pt}
    
  \resumeSubheading
    {Huawei Noah’s Ark Lab}{Shenzhen}
    {Research Intern $|$ Advisor: Dr. Zhitang Chen \& Dr. Jie Chuai}{2020/10 \textbf{--} 2021/04}
      \resumeItemListStart
          \resumeItem{Collaborative Optimization for Large-scale 4G LTE Cell Networks}
          \resumeItem{Scenario-based Optimization for High-Dimension 5G RF Parameters}
      \resumeItemListEnd
      \vspace{5pt}

  \resumeSubheading
    {Didi Chuxing \& SYSU Research Cooperation Program}{Guangzhou}
    {Research Assistant $|$ Advisor: Prof. Renxin Zhong}{2018/11 \textbf{--} 2020/05}
      \resumeItemListStart
      \resumeItem{A Multi-Agent Reinforcement Learning Approach for Online Vehicle Dispatching}
      \resumeItem{Dynamic Spatial-Temporal Pricing for Supply-demand Regulations of Ride-sourcing Market}
    \resumeItemListEnd
    \vspace{5pt}

    \resumeSubheading
        {Guangdong Key Laboratory of Intelligent Transportation Systems}{Guangzhou}
        {Research Assistant $|$ Advisor: Prof. Renxin Zhong}{2018/04 \textbf{--} 2018/10}
          \resumeItemListStart
              \resumeItem{The Calibration of First-Order Macroscopic Traffic Models Using MF-CEM}
        \resumeItemListEnd
        \vspace{5pt}

  \resumeSubHeadingListEnd













%----------- Publication -----------
\section{\LARGE Conference Proceedings}{$\star$: Co-first; $\dag$: Co-corresponding}
\vspace{5pt}
\resumeSubHeadingListStart
    {

    \item{$\rhd$
    {Fast Projection-Free Approach (without Optimization Oracles) for Optimization over Compact Convex Set} \\ 
    Chenghao Liu, \underline{\textbf{Enming Liang}}$^{\dag}$, Minghua Chen$^{\dag}$. \\
    In Proceedings of The Thirty-Ninth Annual Conference on Neural Information Processing Systems (\textbf{NeurIPS 2025}). \textbf{Spotlight}.
    }
    \vspace{5pt}


    \item{$\rhd$
      Efficient Bisection Projection to Ensure NN Solution Feasibility for Optimization over General Set. \\
      \underline{\textbf{Enming Liang}}, Minghua Chen. \\
      In Proceedings of the Forty-second International Conference on Machine Learning (\textbf{ICML'2025}).
      }
    \vspace{5pt}


      \item{$\rhd$
       DFF: Decision-Focused Fine-tuning for Smarter Predict-then-Optimize with Limited Data. \\
       Jiaqi Yang$^{\star}$, \underline{\textbf{Enming Liang}}$^{\star}$, Zicheng Su, Zhichao Zou, Zhen Peng, Jiecheng Guo, Kun An, Wanjing Ma.\\
       In Proceedings of the AAAI Conference on Artificial Intelligence (\textbf{AAAI'2025}). \textbf{Oral}.
      }
      \vspace{5pt}


      \item{$\rhd$
        Characterizing ResNet's Universal Approximation Capability. \\
        Chenghao Liu, \underline{\textbf{Enming Liang}}, Minghua Chen.\\
        In Proceedings of the Forty-first International Conference on Machine Learning (\textbf{ICML'2024}).
      }
      \vspace{5pt}


      \item{$\rhd$
        Generative Learning for Solving Non-Convex Problem with Multi-Valued Input-Solution Mapping. \\
        \underline{\textbf{Enming Liang}}, Minghua Chen.\\
        In Proceedings of the Twelfth International Conference on Learning Representations (\textbf{ICLR'2024}).
      }
      \vspace{5pt}
    
    
      \item{$\rhd$
        Low Complexity Homeomorphic Projection to Ensure NN Solution Feasibility for Optimization over (Non-)Convex Set. \\
        \underline{\textbf{Enming Liang}}, Minghua Chen, Steven H. Low.\\
        In Proceedings of the Fortieth International Conference on Machine Learning (\textbf{ICML'2023}).
        }
      \vspace{5pt}
    
      \item{$\rhd$
        OAM: an Option-Action Reinforcement Learning Framework for Universal Multi-Intersection Control. \\
        \underline{\textbf{Enming Liang}}, Zicheng Su, Chilin Fang, Renxin Zhong.\\
        In Proceedings of the AAAI Conference on Artificial Intelligence (\textbf{AAAI'2022}). \textbf{Oral}.
      }
      \vspace{5pt}
      }
  \resumeSubHeadingListEnd






  \section{\LARGE Workshop Papers} 
  \vspace{5pt}
  \resumeSubHeadingListStart
    {
      \item{$\rhd$
        On the Expressiveness of Graph Neural Network for Solving Second-Order Cone Programming. \\
        Ruizhe Li, \underline{\textbf{Enming Liang}}$^{\dag}$, Minghua Chen$^{\dag}$. \\
        \textbf{NeurIPS 2025} $|$ ScaleOPT workshop.
      }
      \item{$\rhd$
        Gauge Flow Matching for Efficient Constrained Generative Modeling over General Convex Set. \\
        Xinpeng Li$^{\star}$, \underline{\textbf{Enming Liang}}$^{\star}$, Minghua Chen. \\
        \textbf{ICLR 2025} $|$ DeLTa workshop $|$ \textbf{Outstanding Short Paper Award}.
      }
      \vspace{5pt}
      \item{$\rhd$
        Solving Chance-Constrained AC-OPF Problems by Neural Network with Bisection-based Projection. \\
        \underline{\textbf{Enming Liang}}$^{*}$, Min Zhou$^{*}$, Jiawei Zhao, Minghua Chen. \\
        \textbf{ACM E-energy 2025} $|$ EnergySP workshop.
      }
      \vspace{5pt}
    }
  \resumeSubHeadingListEnd
  

  

  \section{\LARGE Journal Publications}
  \vspace{5pt}
  \resumeSubHeadingListStart
    {

    \item{$\rhd$
    Partially Permutation-Invariant Neural Network for Solving Two-Stage Stochastic AC-OPF Problem. \\
    Min Zhou, {\underline{\textbf{Enming Liang}}$^{\dag}$, Minghua Chen$^{\dag}$, Steven Low. \\
    IEEE Transactions on Power Systems (\textbf{TPWRS}). 2025.}
  }
  \vspace{5pt}

    \item{$\rhd$
      Homeomorphic Projection to Ensure Neural-Network Solution Feasibility for Constrained Optimization. \\
      {\underline{\textbf{Enming Liang}}, Minghua Chen, Steven H. Low. \\
      Journal of Machine Learning Research (\textbf{JMLR}). 2024}
    }
    \vspace{5pt}
  
    \item{$\rhd$
      Hierarchical Control for Stochastic Network Traffic with Reinforcement Learning. \\
      Zicheng Su, Andy H.F. Chow, Chilin Fang, \underline{\textbf{Enming Liang}}, Renxin Zhong. \\
      Transportation Research Part B: Methodological (\textbf{TRB}). 2023. 
    }
    \vspace{5pt}
  
    \item{$\rhd$
      An Integrated Reinforcement Learning and Centralized Programming Approach for Online Taxi Dispatching. \\
      {\underline{\textbf{Enming Liang}}, Kexin Wen, William H.K. Lam, Agachai Sumalee, Renxin Zhong. \\
      IEEE Transactions on Neural Networks and Learning Systems (\textbf{IEEE TNNLS}). 2021.}
    }
    \vspace{5pt}
  
    \item{  $\rhd$
      Adaptive Signal Control for Bus Service Reliability with Connected Vehicle Technology via Reinforcement Learning. \\
      Andy H.F. Chow, Zicheng Su, \underline{\textbf{Enming Liang}}, Renxin Zhong. \\
      Transportation Research Part C: Emerging Technologies (\textbf{TRC}). 2021.
    }
    \vspace{5pt}
    \item{$\rhd$
      Neuro-Dynamic Programming for Optimal Control of Macroscopic Fundamental Diagram Systems. \\
      Zicheng Su, Andy H.F. Chow, Nan Zheng, Yunping Huang, \underline{\textbf{Enming Liang}}, Renxin Zhong. \\
      Transportation Research Part C: Emerging Technologies (\textbf{TRC}). 2020.
    }
    \vspace{5pt}
  
    %   \item{
    %   Min Zhou, {\underline{\textbf{Enming Liang}}, Minghua Chen, Steven Low. Partially Permutation-Invariant Neural Network for Solving Two-Stage Stochastic AC-OPF Problem. (Under review). 2024.}
    % }
    % \vspace{5pt}
    % \item{
    %   {\underline{\textbf{Enming Liang}}, Minghua Chen, Steven H. Low. Homeomorphic Projection to Ensure Neural-Network Solution Feasibility for Constrained Optimization. Journal of Machine Learning Research (\textbf{JMLR}). 2024}
    % }
    % \vspace{5pt}
  
    % \item{
    %   Zicheng Su, Andy H.F. Chow, Chilin Fang, \underline{\textbf{Enming Liang}}, Renxin Zhong. Hierarchical Control for Stochastic Network Traffic with Reinforcement Learning. Transportation Research Part B: Methodological (\textbf{TRB}). 2023. 
    % }
    % \vspace{5pt}
  
    % \item{
    %   {\underline{\textbf{Enming Liang}}, Kexin Wen, William H.K. Lam, Agachai Sumalee, Renxin Zhong. An Integrated Reinforcement Learning and Centralized Programming Approach for Online Taxi Dispatching. IEEE Transactions on Neural Networks and Learning Systems (\textbf{IEEE TNNLS}). 2021.}
    % }
    % \vspace{5pt}
  
    % \item{  
    %   Andy H.F. Chow, Zicheng Su, \underline{\textbf{Enming Liang}}, Renxin Zhong. Adaptive Signal Control for Bus Service Reliability with Connected Vehicle Technology via Reinforcement Learning. Transportation Research Part C: Emerging Technologies (\textbf{TRC}). 2021.
    % }
    % \vspace{5pt}
    % \item{
    %   Zicheng Su, Andy H.F. Chow, Nan Zheng, Yunping Huang, \underline{\textbf{Enming Liang}}, Renxin Zhong. Neuro-Dynamic Programming for Optimal Control of Macroscopic Fundamental Diagram Systems. Transportation Research Part C: Emerging Technologies (\textbf{TRC}). 2020.
    % }
    % \vspace{5pt}
    }
  
  \resumeSubHeadingListEnd














\section{\LARGE Tutorials}
\vspace{5pt}
\resumeSubHeadingListStart
  {\item{
    $\rhd$\href{https://githubtocolab.com/climatechange-ai-tutorials/optimal-power-flow/blob/main/AI_for_Optimal_Power_Flow.ipynb}{AI for Optimal Power Flow Tutorial}.\\
    {\underline{\textbf{Enming Liang}}, 
    Priya L. Donti, and 
    Minghua Chen.\\
      \textbf{Climate Change AI Summer School}. 2024.}
  \vspace{5pt}
  }}
\resumeSubHeadingListEnd
  









%----------- Proposal & Grants -----------
\section{\LARGE Grants \& Funds}
\vspace{5pt}
\resumeSubHeadingListStart

\resumeSubheading
{CCF-DiDi GAIA Collaborative Research Funds 2025}{}
{Co-PI $|$ (PI: Dr. Zicheng Su from Tongji University)}{}
  \resumeItemListStart
      \resumeItem{Optimal Subsidy Design under Uncertainty}
\resumeItemListEnd
\vspace{5pt}

\resumeSubheading
{CCF-DiDi GAIA Collaborative Research Funds 2024}{}
{Co-PI $|$ (PI: Dr. Zicheng Su from Tongji University)}{}
  \resumeItemListStart
      \resumeItem{Optimal Subsidy Design for Ride-Sourcing Platform}
\resumeItemListEnd
\vspace{5pt}

\resumeSubheading
{CCF-DiDi GAIA Collaborative Research Funds 2023}{}
{Co-PI $|$ (PI: Dr. Zicheng Su from Tongji University)}{}
  \resumeItemListStart
      \resumeItem{Decision-Focused Learning for Ride-Sourcing Platform}
\resumeItemListEnd
\vspace{5pt}
\resumeSubHeadingListEnd







%----------- AWARDS & ACHIEVEMENTS -----------


\section{\LARGE Competition Prizes}
\vspace{5pt}
\resumeSubHeadingListStart
\resumeSubheading
{\href{https://www.biendata.xyz/competition/kdd_didi/winners/}{KDD CUP: Learning to Dispatch and Reposition on a Mobility-on-Demand Platform}}{2020}
{Top 2 (0.1\%) $|$ Solo winner  }{}
\vspace{5pt}

\resumeSubheading
{Huawei \& ICAPS: Dynamic Pickup and Delivery Problem Competition}{2021}
{Silver Prize (0.2\%)}{}
\vspace{5pt}

\resumeSubheading
{MeiTuan 1st Low-Altitude Economy Flight Management Challenge}{2024}
{Silver Prize (1\%)}{}
\vspace{5pt}


\resumeSubHeadingListEnd







%----------- AWARDS & ACHIEVEMENTS -----------
\section{\LARGE Awards \& Honors}
\vspace{5pt}
\resumeSubHeadingListStart

\resumeSubSubheading
{{Top Reviewer Award in NeurIPS 2024}}{2024}
\vspace{5pt}

\resumeSubSubheading
{Outstanding Academic Performance Award $|$ CityU HK}{2023}
\vspace{5pt}

\resumeSubSubheading
{Excellence Award in \textit{Star of Tomorrow Internship Program}, MSRA}{2022}
\vspace{5pt}

\resumeSubSubheading
{Research Tuition Scholarship $|$ CityU HK}{2022 \& 2023}
\vspace{5pt}


\resumeSubSubheading
{Outstanding Undergraduate Thesis $|$ SYSU}{2020}
\vspace{5pt}

\resumeSubSubheading
{National Scholarship  $|$ China}{2020}
\vspace{5pt}
 
\resumeSubHeadingListEnd




%----------- AWARDS & ACHIEVEMENTS -----------
\section{\LARGE Tutorial \& Teaching}
\vspace{5pt}
\resumeSubHeadingListStart
\resumeSubSubheading
{Teacher at CityU, HK}{2025-2027}
\resumeItemListStart
\resumeItem{2025/26 Semester B}{$|$  }{ SDSC3060 Operations Research}
\resumeItemListEnd
\vspace{5pt}


\resumeSubSubheading
{Teaching Assistant at CityU, HK}{2021-2024}
\resumeItemListStart
\resumeItem{2021/22 Semester B}{$|$  }{ SDSC3060 Operations Research}
\vspace{1pt}
\resumeItem{2022/23 Semester A}{$|$  }{ SDSC3019 Intro to Networked Life \& DS}
\vspace{1pt}
\resumeItem{2022/23 Semester B}{$|$  }{ SDSC6014 Networked Life \& Data Science}
\vspace{1pt}
\resumeItem{2023/24 Semester B}{$|$  }{ SDSC6014 Networked Life \& Data Science}
\resumeItemListEnd


\vspace{5pt}
\resumeSubHeadingListEnd


\section{\LARGE Professional Services}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeSubheading
{{Conference Reviewer}}{2023-2025}
{}{}
\vspace{-15pt}
\resumeItemListStart
\resumeItem{International Conference on Machine Learning (ICML)}{2025}
\resumeItem{International Conference on Learning Representations (ICLR)}{2025}
\resumeItem{Conference on Neural Information Processing Systems (NeurIPS)}{2024}
\resumeItem{Annual AAAI Conference on Artificial Intelligence (AAAI)}{2023/2024/2025}
\resumeItem{International Conference on Artificial Intelligence and Statistics (AISTATS)}{2025}
\resumeItemListEnd

\resumeSubheading
{{Journal Reviewer}}{2023-2025}
{}{}
\vspace{-15pt}
\resumeItemListStart
\resumeItem{Transcation on Machine Learning Research (TMLR)}
\resumeItem{Transportation Research Part E}
\resumeItem{Transportmetrica B}
\resumeItem{Neural Computing}
\resumeItem{IEEE Power Engineering Letters}
\resumeItemListEnd

\resumeSubHeadingListEnd












%----------- SKILLS -----------

% \section{Skills}
%   \vspace{2pt}
%   \resumeSubHeadingListStart
%     \small{\item{
%         \textbf{Languages:}{ Chinese (Native), English (TOEFL 107, GRE 325)} \\ \vspace{3pt}
%         \textbf{Programming:}{ Python, MATLAB} \\ \vspace{3pt}
%     }}
%   \resumeSubHeadingListEnd



%----------- RELEVANT COURSEWORK -----------

% \section{Relevant Coursework}
%   \vspace{2pt}
%   \resumeSubHeadingListStart
%     \small{\item{
%         \textbf{Major coursework:}{ Calculus I-II, Matrix Theory, Differential Equations, Materials Science, Electrical Circuits I-II, Digital System Design, Numerical Methods, Probability Theory, Electronics I-II, Signals and Systems, Electromagnetic Field Theory, Energy Conversion, System Dynamics and Control, Communication Engineering} \\ \vspace{3pt}
        
%         \textbf{Minor coursework:}{ Discrete Computational Structures, Introduction to Object-Oriented Programming, Data Structures and Algorithms}
%     }}
%   \resumeSubHeadingListEnd



%----------- CERTIFICATES -----------

% \section{Certificates}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Procter \& Gamble VIA Certificate Program}{Feb 2022}{Business Skills, Data and Digital Skills, Project Management and Personal Productivity}
    
  % \resumeSubHeadingListEnd



%----------- ORGANIZATIONS -----------

% \section{Organizations}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Institute of Electrical and Electronics Engineers (IEEE)}{Feb 2022 -- Present}{Student Member}
    
  % \resumeSubHeadingListEnd



%----------- HOBBIES -----------

% \section{Hobbies}
  % \resumeSubHeadingListStart
    % \small{\item{Swimming, Fitness, Eight-ball}}
  % \resumeSubHeadingListEnd



%----------- REFERENCES -----------

% \section{References}
  % \resumeSubHeadingListStart
    
  % \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
